\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}

### 2019-09-23 Documentation/Response_to_AEJ_Editor.tex

This letter summarizes our responses to the comments that we received from you and the referees after our resubmission to the \textit{American Economic Journal: Macroeconomics}. We truly appreciate it that you have conditionally accepted our paper. Overall, it has been a wonderful experience working with the \textit{AEJ: Macro}. It was very enjoyable revising our paper following the guidance we received from you and the referees.

We have taken the expositional comments from both referees. We have also followed your advice on leaving the CES case in Appendix J. Our responses in detail are as follows.

\begin{flushleft}
\textbf{Response to Referee 1's Comments:}
\end{flushleft}

\begin{enumerate}
    \item
    We thank Referee 1 for mentioning the paper by \citet{Heetal:2019} to us. It is clear that the paper used a different dataset, which has a panel structure. However, we were not able to trace the exact source of the dataset based on the information in the paper. The dataset does not seem to have an official English translation for its name. Hence we had a hard time trying to pin down the source by its name. Our educated guess is that they were using the firm-level data from \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.

### 2019-09-23 Documentation/Response_to_AEJ_Editor.tex

This letter summarizes our responses to the comments that we received from you and the referees after our resubmission to the \textit{American Economic Journal: Macroeconomics}. We truly appreciate it that you have conditionally accepted our paper. Overall, it has been a wonderful experience working with the \textit{AEJ: Macro}. It was very enjoyable revising our paper following the guidance we received from you and the referees.

We have taken the expositional comments from both referees. We have also followed your advice on leaving the CES case in Appendix J. Our responses in detail are as follows.

\begin{flushleft}
\textbf{Response to Referee 1's Comments:}
\end{flushleft}

\begin{enumerate}
    \item
    We thank Referee 1 for mentioning the paper by \citet{Heetal:2019} to us. It is clear that the paper used a different dataset, which has a panel structure. However, we were not able to trace the exact source of the dataset based on the information in the paper. The dataset does not seem to have an official English translation for its name. Hence we had a hard time trying to pin down the source by its name. Our educated guess is that they were using the firm-level data from the \textit{Annual Statistic Report on Environment in China} (in Chinese \begin{CJK}{GBK}{kai}中国环境统计年报\end{CJK}), but we cannot be 100\% sure.

@@

    \item
    \textit{Model}
    \begin{enumerate}[(1)]
        \item
        We have explained what the superscripts $c$ and $d$ refer to when they first appear in the model section; please see the beginning of the second paragraph of part \textit{Household} in Section II.A (page 13) of our new draft. Specifically, the superscript $c$ refers to the non-polluting sector, and $d$ refers to the polluting sector.
        \item
        In our initial submission, our model had one sector and two types of treatment technologies, so we used the index $i=0,1$ to denote the type of treatment technology ($i=1$ for clean technology). In our version, there were two sectors in the model, so we used $i=0,1$ to denote the treatment technologies and $i=c,d$ to denote the sectors. It seems that the use of $i$ in both places has caused some confusion, hence we use the index $j=0,1$ in our new draft. We apologize for the confusion. The $j$ superscript is needed though, as there are a few technology-specific variables that we refer to.
    \end{enumerate}

    \item
    \textit{Quantitative Exercises}

    We sincerely appreciate it that Referee 3 finds the results in Appendix J interesting. Indeed, this exercise is inspired by the referee's comments. We considered this suggestion very carefully; however, we decided to leave these results in Appendix J as they are now for the following reasons. First, the firm-level data suggest that there are severe correlated distortions in both the polluting and non-polluting sectors. Therefore, we think that it is more natural to consider removing distortions from both sectors. Second, when we remove the correlated distortions from the polluting sector only, the results depend critically on the elasticity of substitution between the two sectors $\rho$. Unfortunately, we have not been able to come up with a good estimate of $\rho$ yet. On the other hand, if we remove distortions from both sectors, the value of $\rho$ has very limited impact on the results.
\end{enumerate}

### 2019-09-23 Documentation/Replication_Instruction.tex
final submission

\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Corresponding Author: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{\normalsize\today}

@@

\begin{enumerate}
    \item
    Table A.1 is produced by the second part of \bcode{Descriptive.R}. All numbers are printed to the terminal.
    \item
    Figure B.1 is generated by Section 1 of \bcode{Empirical\_Appendix.R}. The four panels are saved respectively as \bcode{./Empirical/Results/FigureB1\_TopLeft.pdf}, \bcode{FigureB1\_TopRight.pdf}, \\ \bcode{FigureB1\_BotLeft.pdf} and \bcode{FigureB1\_BotRight.pdf}.
    \item
    Section 2 of \bcode{Empirical\_Appendix.R} produces the results in Appendix C.1. The beginning of that section first runs the regression of intensity to size by industry. The regression results are printed to the terminal, which are exactly the results reported in Table C.1. The five panels of Figure C.1 are then exported to \bcode{./Empirical/Results/} with the names \bcode{FigureC1\_TopLeft.pdf}, \\ \bcode{FigureC1\_TopRight.pdf}, \bcode{FigureC1\_MidLeft.pdf}, \bcode{FigureC1\_MidRight.pdf} and \\ \bcode{FigureC1\_BotLeft.pdf}. Notice that the bottom-right panel is simply Figure 1 in the main text. The code then repeats the exercise for the manufacturing sector as a whole. Results of the un-numbered regressions on Pages 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.

>>>>

\title{\vspace{-1cm}\Large{\textsf{The Size Distribution of Firms and Industrial Water Pollution: A Quantitative Analysis of China} \\ \textsf{Replication Instructions}}}
\author{
  \normalsize{{Ji Qi}} \\
  \normalsize{{Chinese Academy of Environmental Science}}
  \and
  \normalsize{{Xin Tang}}\footnote{Please send all correspondence to: zjutangxin@gmail.com} \\
  \normalsize{{Wuhan University}} \\
  \normalsize{{International Monetary Fund}}
  \and
  \normalsize{{Xican Xi}} \\
  \normalsize{{Fudan University}}
}
\date{\normalsize\today}

@@

\begin{enumerate}
    \item
    Table A.1 is produced by the second part of \bcode{Descriptive.R}. All numbers are printed to the terminal.
    \item
    Figure B.1 is generated by Section 1 of \bcode{Empirical\_Appendix.R}. The four panels are saved respectively as \bcode{./Empirical/Results/FigureB1\_TopLeft.pdf}, \bcode{FigureB1\_TopRight.pdf}, \\ \bcode{FigureB1\_BotLeft.pdf} and \bcode{FigureB1\_BotRight.pdf}.
    \item
    Section 2 of \bcode{Empirical\_Appendix.R} produces the results in Appendix C.1. The beginning of that section first runs the regression of intensity to size by industry. The regression results are printed to the terminal, which are exactly the results reported in Table C.1. The five panels of Figure C.1 are then exported to \bcode{./Empirical/Results/} with the names \bcode{FigureC1\_TopLeft.pdf}, \\ \bcode{FigureC1\_TopRight.pdf}, \bcode{FigureC1\_MidLeft.pdf}, \bcode{FigureC1\_MidRight.pdf} and \\ \bcode{FigureC1\_BotLeft.pdf}. Notice that the bottom-right panel is simply Figure 1 in the main text. The code then repeats the exercise for the manufacturing sector as a whole. Results of the un-numbered regressions on Pages 7, 9 and 10 (the last one) are then printed to the terminal, with Figure C.2 exported to \bcode{./Empirical/Results/FigureC2.pdf}.
